Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-11 06_bat_data.Rmd
atlastools call
remove install code

@@

## Install `atlastools` from Github.

`atlastools` is available from Github and is archived on Zenodo [@gupte2020a].
It can be installed using `remotes` or `devtools`. Here we use the `remotes` function `install_github`.

```{r install_atlastools}
install.packages("remotes")

# installation using remotes
remotes::install_github("pratikunterwegs/atlastools")
```

@@

```{r}
data_clean <- fwrite(rbindlist(data_smooth),
  file = "data/data_bat_smooth.csv"
)
```

>>>>

# atlastools
library(atlastools)

@@

@@

```{r}
fwrite(rbindlist(data_smooth),
  file = "data/data_bat_smooth.csv"
)
```
